Shades of Green in the Swedish Forest-Based Bioeconomy Transition

### 2023-09-25 docs/reports/paper/paper1.qmd
update sum_bioeconomy name in paper1.qmd

codes_df = pd.read_sql(
    "SELECT * FROM classification_codes", conn
)

codes_df["Category"] = codes_df["Category"].str.strip()
uncertain_eco = {"Code":"000", "Category":"Unsure"}
codes_df = codes_df.append(uncertain_eco, ignore_index=True)

codes_df = codes_df[~codes_df["Code"].duplicated(keep='last')
]

codes_df =codes_df.set_index("Code")
```

@@

```{python}
#| label: Total SWINNO Innovation
#| output: asis

@@

display(Markdown(
    f"The SWINNO database used here contains {n_swinno} innovations commercialized between {year_min} and {year_max}. It is constructed according to  literature-based innovation output (LBIO) method using Swedish source material [@sjoo2014DatabaseSwedishInnovations]. This method relies on the judgment of editiors and journalists at trade journals and hence captures what can be described as significant innovation."
))
```

@@

```{python}
#| label: Number Bioeconomy Innovation
#| output: asis

sum_bioeconomy_visions = swinno["bioeconomy"].sum()

display(
    Markdown(
        f"Querying the SWINNO database for forest based bioeconomy innovations initally yields {sum_bioeconomy_visions} innovations. This number includes false positives from substrings matching keywords included in the search. While there is no indication that these false positives are non-randomly distributed across time and sectors, the following analysis for bioeconomy innovation trends at large needs to be viewed in the light of this being unlceaned data. Where the analysis turns to specific bioeconomy visions, only clean and certain cases are discussed."
    )
)
```

```{python}
#| label: Query eco-innovation

@@

```{python}
#| label: Calculate Bioeconomy Share

@@

count_certain_bioeconomy_visions = (
    certain_bioeconomy_visions
    .groupby(["year", "bioeconomy_vision"])
    .size()
    .reset_index(name="count")
)

total_certain_bioeconomy_visions = (count_certain_bioeconomy_visions
        .groupby("bioeconomy_vision")
        .agg("sum", numeric_only=True)
        .sort_values("count", ascending=False)
        .reset_index()
)

@@

```{python}
#| label: Number of Uncertains
#| output: asis

@@

n_certain_bioeconomy_visions = certain_bioeconomy_visions['sinno_id'].nunique()

certain_bioeconomy_visions_min_year = certain_bioeconomy_visions['year'].min()

certain_bioeconomy_visions_max_year = certain_bioeconomy_visions['year'].max()

@@

display(
    Markdown(
        f"This leaves {n_certain_bioeconomy_visions} innovations have been classified for the period between {certain_bioeconomy_visions_min_year} and {certain_bioeconomy_visions_max_year}. With {n_most_bioeconomy_vision} innovations, the {total_certain_bioeconomy_visions.iloc[0, 0]} has the most associated innovations. Next the {total_certain_bioeconomy_visions.iloc[1, 0]} was associated with {total_certain_bioeconomy_visions.iloc[1,1]}, while {total_certain_bioeconomy_visions.iloc[2,1]} and  {total_certain_bioeconomy_visions.iloc[3,1]} innovation were classified as {total_certain_bioeconomy_visions.iloc[2,0]} and {total_certain_bioeconomy_visions.iloc[3,0]}, respectively. Note that the sum by category will not yield the total number of classified innovations, as one innovation can be associated with more than one bioeconomy vision."
    ))

@@

n_bioecology_vision = count_certain_bioeconomy_visions.loc[count_certain_bioeconomy_visions["bioeconomy_vision"] == "Bioecology Vision", "count"].sum()

@@

```{python}
#| label: fig-eco_innovation_by_bioeconomy_vision
#| fig-cap: Count of Eco-Innovation Types by Bioeconomy Vision
p = plot_eco_innovation_by_bioeconomy_vision(eco_innovation_by_bioeconomy_visions, codes_df)

>>>>

codes_df = pd.read_sql("SELECT * FROM classification_codes", conn)

codes_df["Category"] = codes_df["Category"].str.strip()
uncertain_eco = {"Code": "000", "Category": "Unsure"}
codes_df = codes_df.append(uncertain_eco, ignore_index=True)

codes_df = codes_df[~codes_df["Code"].duplicated(keep="last")]

codes_df = codes_df.set_index("Code")
```

@@

```{python}
# | label: Total SWINNO Innovation
# | output: asis

@@

display(
    Markdown(
        f"The SWINNO database used here contains {n_swinno} innovations commercialized between {year_min} and {year_max}. It is constructed according to  literature-based innovation output (LBIO) method using Swedish source material [@sjoo2014DatabaseSwedishInnovations]. This method relies on the judgment of editiors and journalists at trade journals and hence captures what can be described as significant innovation."
    )
)
```

@@

```{python}
# | label: Number Bioeconomy Innovation
# | output: asis

sum_bioeconomy_innovations = swinno["bioeconomy"].sum()

display(
    Markdown(
        f"Querying the SWINNO database for forest based bioeconomy innovations initally yields {sum_bioeconomy_innovations} innovations. This number includes false positives from substrings matching keywords included in the search. While there is no indication that these false positives are non-randomly distributed across time and sectors, the following analysis for bioeconomy innovation trends at large needs to be viewed in the light of this being unlceaned data. Where the analysis turns to specific bioeconomy visions, only clean and certain cases are discussed."
    )
)
```

```{python}
# | label: Query eco-innovation

@@

```{python}
# | label: Calculate Bioeconomy Share

@@

count_certain_bioeconomy_visions = (
    certain_bioeconomy_visions.groupby(["year", "bioeconomy_vision"])
    .size()
    .reset_index(name="count")
)

total_certain_bioeconomy_visions = (
    count_certain_bioeconomy_visions.groupby("bioeconomy_vision")
    .agg("sum", numeric_only=True)
    .sort_values("count", ascending=False)
    .reset_index()
)

@@

```{python}
# | label: Number of Uncertains
# | output: asis

@@

n_certain_bioeconomy_visions = certain_bioeconomy_visions["sinno_id"].nunique()

certain_bioeconomy_visions_min_year = certain_bioeconomy_visions["year"].min()

certain_bioeconomy_visions_max_year = certain_bioeconomy_visions["year"].max()

@@

display(
    Markdown(
        f"This leaves {n_certain_bioeconomy_visions} innovations have been classified for the period between {certain_bioeconomy_visions_min_year} and {certain_bioeconomy_visions_max_year}. With {n_most_bioeconomy_vision} innovations, the {total_certain_bioeconomy_visions.iloc[0, 0]} has the most associated innovations. Next the {total_certain_bioeconomy_visions.iloc[1, 0]} was associated with {total_certain_bioeconomy_visions.iloc[1,1]}, while {total_certain_bioeconomy_visions.iloc[2,1]} and  {total_certain_bioeconomy_visions.iloc[3,1]} innovation were classified as {total_certain_bioeconomy_visions.iloc[2,0]} and {total_certain_bioeconomy_visions.iloc[3,0]}, respectively. Note that the sum by category will not yield the total number of classified innovations, as one innovation can be associated with more than one bioeconomy vision."
    )
)

@@

n_bioecology_vision = count_certain_bioeconomy_visions.loc[
    count_certain_bioeconomy_visions["bioeconomy_vision"] == "Bioecology Vision",
    "count",
].sum()

@@

```{python}
# | label: fig-eco_innovation_by_bioeconomy_vision
# | fig-cap: Count of Eco-Innovation Types by Bioeconomy Vision
p = plot_eco_innovation_by_bioeconomy_vision(
    eco_innovation_by_bioeconomy_visions, codes_df
)
